White Dwarf Mergers on Adaptive Meshes\\ I. Methodology and Code Verification

### 2015-12-15 papers/wdmerger_I/paper.tex
Acknowledge Stony Brook IACS for its support

This research has made use of the AstroBetter blog and wiki. 
This research has made use of NASA's Astrophysics Data System 
Bibliographic Services.

This research was supported by NSF award AST-1211563. An
award of computer time was provided by the Innovative and Novel
Computational Impact on Theory and Experiment (INCITE) program.  This
research used resources of the Oak Ridge Leadership Computing Facility
located in the Oak Ridge National Laboratory, which is supported by
the Office of Science of the Department of Energy under Contract
DE-AC05-00OR22725. Projects AST006 and AST106 supported use of the ORNL/Titan resource. 
This research is part of the Blue Waters sustained-petascale computing project, 
which is supported by the National Science Foundation (awards OCI-0725070 
and ACI-1238993) and the state of Illinois. Blue Waters is a joint 
effort of the University of Illinois at Urbana-Champaign and its 
National Center for Supercomputing Applications.
This research used resources of the National Energy Research Scientific Computing
Center, which is supported by the Office of Science of the
U.S. Department of Energy under Contract No. DE-AC02-05CH11231.  
This work used the Extreme Science and Engineering Discovery Environment (XSEDE), 
which is supported by National Science Foundation grant number ACI-1053575. 
Project AST100037 supported use of the resources NICS/Kraken and NICS/Darter.

>>>>

This research was supported by NSF award AST-1211563. An
award of computer time was provided by the Innovative and Novel
Computational Impact on Theory and Experiment (INCITE) program.  This
research used resources of the Oak Ridge Leadership Computing Facility
located in the Oak Ridge National Laboratory, which is supported by
the Office of Science of the Department of Energy under Contract
DE-AC05-00OR22725. Projects AST006 and AST106 supported use of the ORNL/Titan resource. 
This research is part of the Blue Waters sustained-petascale computing project, 
which is supported by the National Science Foundation (awards OCI-0725070 
and ACI-1238993) and the state of Illinois. Blue Waters is a joint 
effort of the University of Illinois at Urbana-Champaign and its 
National Center for Supercomputing Applications.
This research used resources of the National Energy Research Scientific Computing
Center, which is supported by the Office of Science of the
U.S. Department of Energy under Contract No. DE-AC02-05CH11231.
Additional support and computer time was provided by the Stony Brook
University Institute for Advanced Computational Science, in particular
through approval to run on its LI-RED cluster.
This work used the Extreme Science and Engineering Discovery Environment (XSEDE), 
which is supported by National Science Foundation grant number ACI-1053575. 
Project AST100037 supported use of the resources NICS/Kraken and NICS/Darter.

This research has made use of NASA's Astrophysics Data System 
Bibliographic Services. In addition, this research has made use
of the AstroBetter blog and wiki.
